Declarative Deployment Reconfiguration of Pulverised Collective Adaptive Systems at Runtime \thanks{Identify applicable funding agency here. If none, delete this.}

### 2023-05-17 paper-2023-acsos-pulverization.tex
Background on deployment and its relationshop with RW sec

\subsection{Deployment and Reconfiguration: Basic Concepts}

The \emph{deployment view} is a well-known architectural viewpoint for software systems,
concerned with the mapping of \emph{software components} to \emph{physical machines}~\cite{DBLP:journals/software/Kruchten95}
 and supported by modelling notations like \emph{UML Deployment diagrams}.
%
Here, we provide a brief introduction to deployment and reconfiguration, based on the conceptual characterisation of~\cite{DBLP:journals/jss/ArcangeliBL15,carzaniga1998characterization}.
%
A \emph{site} is a set of computers (\emph{hosts}) that may host a \emph{software system}, i.e., a coherent collection of artifacts.
%
\emph{(Software) Deployment} is the process of moving and making a software product available and operational from one or more \emph{producer sites} to a target \emph{deployment domain} (i.e., a set of \emph{consumer sites}).
%
The \emph{deployment plan} defines 
 the mapping between the software system
 and the deployment domain,
 augmented with further information (e.g., metadata).
%
Deployment-related activities 
 include: (i) \emph{release/update} of the software system at the producer site;
 (ii) \emph{installation/deinstallation} at/from the consumer sites;
 (iii) \emph{activation/deactivation}, for starting/stopping the components;
 (iv) \emph{reorganisation} of the software system;
 and (v) \emph{redistribution}, i.e., changing the deployment plan.

@@

This work provides 
 \acp{dsl}
 for specifying 
 distributed systems (partitioned according to the 
 pulverisation model)
 and
 corresponding deployment plans,
 and a framework for executing
 deployment plans and reconfigurations.
%
A way to structure all this 
 is by using the analytical framework of~\cite{DBLP:journals/jss/ArcangeliBL15},
  where the problem of (automatic) deployment of distributed software system is studied by considering
 (i) the nature of software to be deployed,
 (ii) the nature of the deployment domain (i.e. the available infrastructure),
 (iii) how the deployment is designed,
 and 
 (iv) how the deployment is performed.
%
Accordingly, 
 we cover related works about
 languages for 
 specifying distributed systems (\Cref{sec:rw:whatsw}),
 languages for specifying infrastructures and deployments (\Cref{sec:rw:depdesc}),
 and
 techniques for automatic deployment and reconfiguration (\Cref{sec:rw:autodep}).

>>>>

\subsection{Deployment and Reconfiguration: Basic Concepts}\label{sec:background:dep}

The \emph{deployment view} is a well-known architectural viewpoint for software systems,
concerned with the mapping of \emph{software components} to \emph{physical machines}~\cite{DBLP:journals/software/Kruchten95}, 
 and supported by modelling notations like \emph{UML Deployment diagrams}.
%
Here, we provide a brief introduction to deployment and reconfiguration, based on the conceptual characterisation of~\cite{DBLP:journals/jss/ArcangeliBL15,carzaniga1998characterization}.
%
A \emph{site} is a set of computers (\emph{hosts}) that may host a \emph{software system}, i.e., a coherent collection of artifacts.
%
\emph{(Software) Deployment} is the process of moving and making a software system available and operational from one or more \emph{producer sites} to a target set of \emph{consumer sites}, also called the \emph{deployment domain}.
%
The \emph{deployment plan} defines 
 the mapping between the software system
 and the deployment domain,
 possibly augmented with further information (e.g., metadata, constraints, preferences).
%
Common deployment-related activities 
 include: (i) \emph{release/update} of the software system at the producer site;
 (ii) \emph{installation/deinstallation} at/from the consumer sites;
 (iii) \emph{activation/deactivation}, for starting/stopping the components;
 (iv) \emph{reorganisation} of the software system;
 and (v) \emph{redistribution}, i.e., changing the deployment plan.
%
According to the analytical framework of~\cite{DBLP:journals/jss/ArcangeliBL15},
  the problem of (automatic) deployment of distributed software system can be addressed by considering
 (i) the nature of the software to be deployed (e.g., how the software system is split into components);
 (ii) the nature of the deployment domain (i.e. the characteristics and topology of the available infrastructure);
 (iii) how the deployment is designed (e.g., how the deployment plan is specified);
 and 
 (iv) how the deployment is performed (e.g., how deployment activities are carried out).
%
Related work covering these issues is provided in \Cref{sec:rw}.

@@

%This work provides 
% \acp{dsl}
% for specifying 
% distributed systems (partitioned according to the 
% pulverisation model)
% and
% corresponding deployment plans,
% and a framework for executing
% deployment plans and reconfigurations.
%
Following the conceptual framework introduced in \Cref{sec:background:dep},
 in this section we cover related work about
 languages for 
 specifying distributed systems (\Cref{sec:rw:whatsw}),
 languages for specifying infrastructures and deployments (\Cref{sec:rw:depdesc}),
 and
 techniques for automatic deployment and reconfiguration (\Cref{sec:rw:autodep}).
